[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

# Results {#sec-results}
Looking at the graphed data and summary statistics, there appears to be a clear decline in the number of opposite-sex couples opting for a religious ceremony across a fifty-year timeframe between 1970 and 2020. For same-sex couples, civil ceremonies have consistently and overwhelmingly been the most popular ceremony type since the legalization of same-sex marriage in 2014.

@@

# Discussion {#sec-discussion}
## Implication: Religiosity has decreased in England and Wales
## Implication: Same-Sex Couples Overwhelmingly Prefer Civil Ceremonies
## Implication: 
## Limitations
## Future Research {#sec-future}

>>>>

# Results {#sec-results}
Looking at the graphed data and summary statistics, there appears to be a clear decline in the number of opposite-sex couples opting for a religious ceremony across a fifty-year time frame between 1970 and 2020. For same-sex couples, civil ceremonies have consistently and overwhelmingly been the most popular ceremony type since the legalization of same-sex marriage in 2014.Looking further into the data sets, it is apparent that preliminary conclusions from the summary data in @sec-data hold true after further analysis.

@@

# Discussion {#sec-discussion}
## Implication: Religiosity has Decreased in England and Wales
## Implication: Fewer Citizens Identify as Christian
## Implication: Same-Sex Couples Overwhelmingly Prefer Civil Ceremonies
## Limitations
## Future Research {#sec-future}
